Von Neumann-Morgenstern and Savage Theorems for Causal Decision Making

### 2020-08-30 Theory_and_decision/Draft/Theory_and_decision_draft.tex
cambios en intro

On the other hand, an important aspect of acting in the world is being able to make decisions under uncertain conditions \citep{bernardo2000bayesian,kahneman2000choices,gilboa2009decision,lake2017building}. \cite{von1944theory} gave an answer for how to make choices if rational preferences are assumed and if the decision maker knows the stochastic relation between actions and outcomes: maximize expected utility. If no such relation is known, then \cite{savage1954the} showed that a rational decision maker must choose \textit{as if} she is maximizing expected utility using a \textit{subjective} probability distribution. Such theorems provide formal criteria for decision making if rationality is assumed.

>>>>

On the other hand, an important aspect of acting in the world is being able to make decisions under uncertain conditions \citep{bernardo2000bayesian,kahneman2000choices,gilboa2009decision,lake2017building}. \cite{von1944theory} gave an answer for how to make choices if rational preferences are assumed, utilities are known, and if the decision maker knows the stochastic relation (i.e., probabilities of events) between actions and outcomes: maximize expected utility. If no such relation is known, then \cite{savage1954the} showed that a rational decision maker must choose \textit{as if} she is maximizing expected utility using a \textit{subjective} probability distribution. Such theorems provide formal criteria for decision making if rationality is assumed.
